25 years of Social Work Research

### 2015-02-22 dataCleaning.Rmd
Minor code cleanup.

#load("/Users/SSW/GitHub/SocialWork100Years/Data/ebscoFULL.R")
#load("/Users/SSW/GitHub/SocialWork100Years/Data/proQuest.R")
#load("/Users/SSW/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")

@@

# Set the working directory
#setwd("/Users/beperron/Git/SocialWorkResearch/Data")
#setwd("/Users/SSW/GitHub/SocialWork100Years/Data")
```

>>>>

#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")

@@

#Combines EbscoHost and ProQUest wrangles and eliminates duplicate article titles

library(dplyr)

  #Creates variable with highest article ID from ebscohost database
  ebscoIDmax<-max(ebscoBWR.df$articleID)

  #Recodes article ID in ProQuest database in advance of merger with ebscohost
  proQuestBWR.df<-mutate(proQuestBWR.df, articleID=articleID+ebscoIDmax)

  #Creates data frames that contain only article ID and titles from respective
  #databases
  ebscoTitles<-filter(ebscoBWR.df, attributes=="article")
  proTitles<-filter(proQuestBWR.df, attributes=="article")

  #Combines titles into single data frame
  jointTitles<-rbind(ebscoTitles, proTitles)

  #Forces article title text to lower case
  jointTitles$record<-tolower(jointTitles$record)

  #Strips out white space and punctuation to ensure small differences
  #in data entry are detected during duplicate elimination
  jointTitles$record<-gsub(" ","", jointTitles$record)

  #punct <- '[]\\?!\"\'#$%&(){}+*/:;,._`|~\\[<=>@\\^-]'
  #JointTitles$record<-gsub(punct, "", JointTitles$record)  
  jointTitles$record<-gsub("[[:punct:]]", "", jointTitles$record)

  jointTitles<- jointTitles[duplicated(jointTitles$record), ]

  #Screen out duplicated records by articleID. The articleID must be used
  #because the duplicate title contains other article attributes
  jointTitles.dup.ID <- jointTitles$articleID

  #Combines EbscoHost and ProQuest Wrangles, and strips out article attributes 
  #from duplicate entries
  combined.DF<-rbind(ebscoBWR.df, proQuestBWR.df)
  combined.DF<-combined.DF[!(combined.DF$articleID %in% jointTitles.dup.ID), ]

# Set the working directory
#setwd("/Users/beperron/Git/SocialWorkResearch/Data")
#setwd("/Users/SSW/Documents/GitHub/SocialWork100Years/Data")
```
